Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-10 presentation/presentation.tex
CF by dominating set algorithm presentation

\usepackage{graphicx}
\usepackage[scale=2]{ccicons}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm, caption}
\usepackage[noend]{algpseudocode}
\usepackage[absolute,overlay]{textpos}
\usepackage{calc}
% \usepackage[texcoord,grid,gridunit=mm,gridcolor=red!10,subgridcolor=green!10]
% {eso-pic}

@@

@@

>>>>

\usepackage{graphicx}
\usepackage[scale=2]{ccicons}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm, caption}
\usepackage[noend]{algpseudocode}
\usepackage[absolute,overlay]{textpos}
\usepackage{calc}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}

% \usepackage[texcoord,grid,gridunit=mm,gridcolor=red!10,subgridcolor=green!10]
% {eso-pic}

@@

  \subsection{Iterated Elimination of Distance-3-Sets}

@@

  \subsection{Bounds for Planar Graphs}
  \begin{frame}
    \frametitle{Bounds on Planar Graphs}

    \only<3>{
      \begin{figure}[h]
        \centering
        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/four.pdf}
        \caption*{A vertex and conflict-free coloring, respectively}
      \end{figure}
    }

    \begin{theorem}
    Every loopless planar graph admits a proper \textbf{vertex coloring} with at most {\color{red} four} distinct colors.
    \end{theorem}

    \begin{theorem}
    Every loopless planar graph admits a \textbf{conflict-free coloring} with at most {\color{red} three} distinct colors.
    \end{theorem}

  \subsection{Dominating Set Algorithm}
  \begin{frame}
    \frametitle{Conflict-Free Coloring via Dominating Set}

    \input{dominating}
  \end{frame}
